experiment 1

### 2021-10-06 experiments/experiment 1/experiment-1.Rmd
one change

```{r eval = FALSE}
display_diversity(
  400, ##seems to be necessary to be smaller than num_div_treatment_levels
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains
)
```

>>>>

```{r}
display_diversity(
  9, ##TEST 
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains
)
```
